---
title: "Eating Out"
author: "Sakana Uthayasegar"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

Is there a difference in frequently eating out percentages based on ethnicity? 

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, include=FALSE}
#race = c("white","black","other")
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Method
According to the data from the bar graph, a Categorical~Numerical Method is performed based on ethnicity, while the amount of times eating out is used as a numerical variable. 

# Results
Whites eat out more, compared to other races. 

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")

```
## graphical results 

The following bar graphs suggests that the white race frequently eat out approximately 5-10% more, compared to blacks and other ethnicity. 

## Numerical description

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1) 
```
The results of this numerical description shows the frequency of eating out compared to blacks and other ethnicity, supporting that white ethnicity frequently eat out opposed to blacks and other ethnicities. 

# Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
Chi squared tests shows the p value of 0.0008179. which is a small value, therefore, the null hypothesis is rejected. 
The fisher exact test proves that the p value is 0.001208, which leads to the rejection of the null hypothesis due to the p-value lesser quantity. 


# Discussion and Conclusion 
According to analysis from University of Chicago, there is a statistical difference between at least two races with the frequency of eating out. Based on the Chi square test results, the null hypothesis is rejected due to the small p-value of 0.0008179. This concludes that there is an overall difference in the frequency of eating out based on ethnicity.  

# Inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```
