---
title: "Eating Out"
author: "Sakana Uthayasegar"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

Is there a difference in frequently eating out percentages based on ethnicity? 

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, include=FALSE}
#race = c("white","black","other")
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Method
According to the data from the bar graph, a Categorical~Numerical Method is performed based on ethnicity, while the amount of times eating out is used as a numerical variable. 

# Results
Whites eat out more, compared to other races. 

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")

```
## graphical results 

These graphs shows that the white race frequently eat out approximately 5-10% more, compared to blacks and other ethnicities. 

## Numerical description

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1) 
```

#inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
#Conclusion 
restate the ? *
According to chicago reports * 
Tuky square test, 
There is a statistical difference in the frequent of eating out depending on the race. 
The P value is so small that I reject the null hypothesis. 
